Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-05-27 tese/intro.tex
need conclusions and abstract

\subsection{Context}   % English
 	Since the early days of human history, we tried to communicate over far locations, from smoke signals to letters delivered by messengers, real-time communications were limited or even nonexistent. Despite all the efforts made to improve communications, written communication could never replace face to face communication.

>>>>

\subsection{Context}   % English
 	Since the early days of Human History, we tried to communicate over far locations, from smoke signals to letters delivered by messengers, real-time communications were limited or even nonexistent. Despite all the efforts made to improve communications, written communication could never replace face to face communication.

### 2015-05-27 tese/method.tex
need conclusions and abstract

\subsection{Scientific Methodology} % Section
Nesta seccao devem explicar como pensam abordar a vossa de tese, tendo em conta o problema, as contribuicoes que se propoem dar, a arquitectura definida.

Caso ja tenham iniciado a implementacao, ao ler esta seccao devemos saber, por exemplo:
\begin{itemize}
\item como procederam as escolhas das ferramentas, linguagens de programacao, ambientes de desenvolvimento, HW.
\item como efectuaram a  sua validacao e que problema ja encontraram
\item como prevem desenvolver a arquitectura proposta: por onde vao comecar, como vao integrar os componentes, que dificuldades esperam encontrar e que estrategias planeam para as ultrapassar
\item como pensam testar a solucao e validar a vossa ideia, que processo vao utilizar durante o desenvolvimento para facilitar a realizacao de testes e a recolha de resultados.
\end{itemize}

Caso ainda nao tenham iniciado a implementacao, ao ler esta seccao devemos saber, por exemplo:
\begin{itemize}
\item se pensam usar um simulador ou fazer um prototipo
\item se vai usar um simulador se ja sabem qual o, ou como pensam escolhe-lo
\item se vao fazer um prototipo, que equipamentos/linguagens de programação vão escolher/usar 
\item como pensam testar a solucao e validar a vossa ideia
\end{itemize}

>>>>

\subsection{Scientific Methodology} % Section

The most important task in order to implement our project is the infrastructure, without it our project wouldn't work. The basic infrastructure will be our first concern, namely the Web Server configuration, ICE and signaling servers.

The Web development can only start after the basic infrastructure configuration. When leading with streams, the infrastructure will be complemented with stream servers.

There will be four prototypes, the first one should implement most of streaming and collaborative functionalities. The second prototype will have the same functionalities but a more friendly user interface which will be tested and reviewed by potential users. The third prototype will be an improvement based on the users feedback. In the final prototype we will improve our system performance.

Briefly, our web application will be tested with real users and unit tests, the system in general will be validated with benchmarks such as analyzing the its behavior and delays by growing the amount of users and data.
